\begin{thebibliography}{99}

    % --- PLC a Priemyselná automatizácia ---
    \bibitem{plc_journal}
    AL-JUMAILY, M. Automation in industry using Programmable Logic Controllers (PLCs). 
    \textit{International Journal of Computer and Communication Engineering}. 2015, roč. 6, s. 924. 
    Dostupné z: \url{https://www.computersciencejournals.com/ijccn/article/83/6-1-1-924.pdf}

    % --- Node-RED a IoT ---
    \bibitem{nodered_iot}
    BLIIOT. Why Node-Red is the Best IoT Development Tool? 
    \textit{Industrial IoT Gateway Blog} [online]. 2024 [cit. 2025-02-20]. 
    Dostupné z: \url{https://bliiot.com/info-detail/why-node-red-is-the-best-iot-development-tool}

    % --- Show Control systémy ---
    \bibitem{showcontrol_comparison}
    BPAV TECHNOLOGY. Crestron vs Extron vs AMX: What Suits Your Project? 
    \textit{BPAV Blog} [online]. 2023 [cit. 2025-02-20]. 
    Dostupné z: \url{https://blog.bpav.global/news-insights/crestron-vs-extron-vs-amx-what-suits-your-project}

    \bibitem{simpson_show}
    SIMPSON, John Huntington. \textit{Show Networks and Control Systems}. 
    2. vyd. New York: Entertainment Technology Press, 2017. ISBN 978-1138090874.

    % --- MQTT Protokol ---
    \bibitem{mqtt_org}
    MQTT.ORG. MQTT: The Standard for IoT Messaging [online]. 
    2024 [cit. 2025-02-20]. Dostupné z: \url{https://mqtt.org/}

    \bibitem{mqtt_comparison}
    CAVLI WIRELESS. MQTT Protocol in IoT: A Guide to Reliable IoT Communication. 
    \textit{IoT Blog} [online]. 2023 [cit. 2025-02-20]. 
    Dostupné z: \url{https://www.cavliwireless.com/blog/nerdiest-of-things/what-is-the-mqtt-protocol}

    % --- Dátové formáty (JSON vs XML) ---
    \bibitem{json_xml}
    CELERDATA. YAML, JSON and XML: A Practical Guide to Choosing the Right Format. 
    \textit{CelerData Blog} [online]. 2024 [cit. 2025-02-20]. 
    Dostupné z: \url{https://celerdata.com/glossary/yaml-json-and-xml-a-practical-guide-to-choosing-the-right-format}

    % --- Hardvér (RPi + ESP32) ---
    \bibitem{rpi_esp32_scada}
    AL-SHUHAIB, T. Low-Cost ESP32, Raspberry Pi, Node-Red, and MQTT Protocol Based SCADA System. 
    \textit{IEEE International Conference on Intelligent Systems}. 2020. 
    Dostupné z: \url{https://www.researchgate.net/publication/347154219}

    % --- DMX512 ---
    \bibitem{dmx_basics}
    SOMERVILLE, I. \textit{DMX512 Stage Lighting Basics}. 
    Scribd Document [online]. 2013 [cit. 2025-02-20]. 
    Dostupné z: \url{https://www.scribd.com/document/132762444/DMX-Beginners-Guide-Rev2}

    % --- NTP a synchronizácia ---
    \bibitem{ntp_rfc}
    MILLS, D. \textit{Network Time Protocol (Version 4)}. 
    RFC 5905. Internet Engineering Task Force, 2010. 
    Dostupné z: \url{https://datatracker.ietf.org/doc/html/rfc5905}

    % --- Web Frameworky (Flask) ---
    \bibitem{flask_django}
    CLOUDWAYS. Django vs Flask: The Best Python Web Framework in 2025? 
    \textit{Cloudways Blog} [online]. 2024 [cit. 2025-02-20]. 
    Dostupné z: \url{https://www.cloudways.com/blog/django-or-flask/}

    % --- Výkonová elektronika (BTS7960) ---
    \bibitem{bts7960}
    INFINEON TECHNOLOGIES. \textit{BTS7960 High Current PN Half Bridge Datasheet} [online]. 
    2004. Dostupné z: \url{https://www.infineon.com/dgdl/Infineon-BTS7960-DS-v01_01-en.pdf}

\end{thebibliography}