\raggedbottom % Vypne roztahovanie medzier medzi polozkami (ZABRAŇUJE OBROVSKÝM DIERAM)
\begin{thebibliography}{99}

    \bibitem{iec61131}
    IEC 61131-3:2013.
    \textit{Programmable Controllers -- Part 3: Programming
    Languages} [online].
    Geneva: IEC, 2013 [cit. 2026-03-15].
    Dostupné z: \url{https://webstore.iec.ch/en/publication/4552}
    %
    \bibitem{john2010plc}
    JOHN, K. H. a~TIEGELKAMP, M.
    \textit{IEC 61131-3: Programming Industrial Automation
    Systems}.
    2. vyd. Berlin: Springer, 2010. ISBN 978-3-642-12014-5.
    Dostupné z:
    \url{https://link.springer.com/book/10.1007/978-3-642-12015-2}

    % --- Výstavníctvo a interaktívne expozície ---

    \bibitem{interactive_small_museums}
    STILLWELL, B.
    Putting the "Play" Back into Display: Interactive Exhibits
    in Small Museums [online].
    Eugene: University of Oregon, 2017 [cit. 2026-03-15].
    Dostupné z: \url{https://scholarsbank.uoregon.edu/server/api/core/bitstreams/810e909e-35d7-4255-8119-dbcd4cc16104/content}
    %
    \bibitem{museum_immersive_design}
    Research on the Strategy and Practical Mechanism of Museum
    Exhibition Space Design Based on Immersive Experience.
    In: \textit{Proceedings of ETMHS 2025} [online]. 2025
    [cit. 2026-03-15].
    Dostupné z: \url{https://webofproceedings.org/proceedings_series/ESSP/ETMHS\%202025/H27.pdf}
    %
    \bibitem{interactive_exhibition_narrations}
    PARTARAKIS, N. a kol. Designing Interactive Exhibitions
    Based on Innovative Narrations Guided by Architectural
    Space and Digital Technologies.
    In: \textit{NODEM 2006 Proceedings} [online]. 2006
    [cit. 2026-03-15].
    Dostupné z: \url{http://repo.nodem.org/uploads/Designing\%20interactive\%20exhibitions\%20based\%20on\%20innovative\%20narrations\%20guided\%20by\%20architectural\%20space\%20and\%20digital\%20technologies.pdf}
    %
    \bibitem{computational_frameworks_art}
    Computational Frameworks for Interactive Multimedia Art
    Installations in Public Spaces using Real Time Digital
    Control and Visualization.
    \textit{PeerJ Computer Science} [online]. 2024
    [cit. 2026-03-15].
    Dostupné z: \url{https://peerj.com/articles/cs-3384.pdf}
    %
    \bibitem{distributed_control_modeling}
    TKÁČIK, M. a kol. Modeling and Analysis of Distributed
    Control Systems: Proposal of a Methodology.
    \textit{Processes} [online]. 2024, roč. 12, č. 1
    [cit. 2026-03-15].
    Dostupné z: \url{https://www.mdpi.com/2227-9717/12/1/5}
    %
    \bibitem{shehade2020}
    SHEHADE, M. a~STYLIANOU-LAMBERT, T. Virtual Reality
    in Museums: Exploring the Experiences of Museum Professionals.
    \textit{Applied Sciences} [online]. 2020, roč. 10, č. 11,
    článok 4031 [cit. 2026-03-20].
    Dostupné z: \url{https://www.mdpi.com/2076-3417/10/11/4031}
    %
    \bibitem{bachi2024}
    BACHI, V. a~kol. Museums and the Post-Digital: Revisiting
    Challenges in the Digital Transformation of Museums.
    \textit{Heritage} [online]. 2024, roč. 7, č. 2,
    s. 890--910 [cit. 2026-03-20].
    Dostupné z: \url{https://www.mdpi.com/2571-9408/7/2/41}

    % --- Bezdrôtové senzorové siete v historických budovách ---

    \bibitem{zonta2010wireless}
    ZONTA, D. a~kol.
    Real-time health monitoring of historic buildings with
    wireless sensor networks.
    \textit{Smart Structures and Systems} [online]. 2010,
    roč. 6, č. 5, s. 595--615 [cit. 2026-03-15].
    Dostupné z: \url{https://shm.cs.illinois.edu/Full\%20Scale\%20Papers/14.\%20Zonta\%20et\%20al.\%202010.pdf}

    % --- Show Control systémy ---

    \bibitem{distributed_av_platform}
    Design and Implementation of Intelligent Audio-Video
    Interaction and Control Platform Based on Distributed
    Architecture.
    In: \textit{MATEC Web of Conferences} [online]. 2021
    [cit. 2026-03-15].
    Dostupné z: \url{https://www.matec-conferences.org/articles/matecconf/pdf/2021/05/matecconf_cscns20_05002.pdf}
    %
    \bibitem{rpi_esp32_scada}
    AL-SHUHAIB, T. Low-Cost ESP32, Raspberry Pi, Node-Red,
    and MQTT Protocol Based SCADA System.
    \textit{IEEE International Conference on Intelligent
    Systems}. 2020.
    Dostupné z:
    \url{https://www.researchgate.net/publication/347154219}
    %
    \bibitem{ciotoli2022}
    CIOTOLI, G. \textit{Digital transformation: perspectives
    from the industrial and cultural heritage studies sectors}.
    Catania: University of Catania, 2022. Dizertačná práca.
    Dostupné z: \url{https://www.iris.unict.it/retrieve/1793e8b3-941f-4603-81ec-4caecd9c0bd2/Tesi\%20dottorato_compressed.pdf}
    %
    \bibitem{medialon_sumble}
    What is Medialon? Competitors, Complementary Techs
    \& Usage.
    \textit{Sumble} [online]. 2024 [cit. 2026-03-15].
    Dostupné z: \url{https://sumble.com/tech/medialon}
    %
    \bibitem{alcornmcbride}
    Alcorn McBride -- Reliable AV Technology for Themed
    Attractions [online]. 2026 [cit. 2026-03-15].
    Dostupné z: \url{https://alcorn.com/}
    %
    \bibitem{alcornmcbride_history}
    Engineering the Invisible Magic: Alcorn McBride at 40.
    \textit{InPark Magazine} [online]. 2024 [cit. 2026-03-15].
    Dostupné z:
    \url{https://www.inparkmagazine.com/109alcornmcbride/}
    %
    \bibitem{huntington2017}
    HUNTINGTON, John. \textit{Show Networks and Control
    Systems}.
    2. vyd. Campbell, CA: Zircon Designs Press, 2017.
    ISBN 978-1138090874.
    %
    \bibitem{simpson_show}
    SIMPSON, R. \textit{Lighting Control: Technology and
    Applications}.
    Taylor \& Francis, 2003. ISBN 978-0240515663.
    %
    \bibitem{dmx_basics}
    SOMERVILLE, I. \textit{DMX512 Stage Lighting Basics}.
    Scribd Document [online]. 2013 [cit. 2025-02-20].
    Dostupné z: \url{https://www.scribd.com/document/132762444/DMX-Beginners-Guide-Rev2}

    % --- Vendor lock-in v IoT a show-control systémoch ---

    \bibitem{noural2019iot}
    NOURAL, A., ATIQUZZAMAN, M. a GAEDKE, M.
    Software-defined networking: architecture, protocols,
    and applications.
    \textit{Journal of Information and Communication
    Technology} [online]. 2019, roč. 15, s. 796--810
    [cit. 2026-03-15].
    Dostupné z: \url{https://www.emerald.com/ftnet/article/15/1-3/1/1334816/Software-defined-networking-architecture-protocols}
    %
    \bibitem{microcontrollers_museum_arxiv}
    PATITUCCI, A. a kol. Interactive Museum Exhibits with
    Microcontrollers: A Use-Case Scenario.
    \textit{arXiv} [online]. 2015 [cit. 2026-03-15].
    Dostupné z: \url{https://arxiv.org/abs/1509.07626}

    % --- MQTT a komunikačné protokoly ---

    \bibitem{mqtt_http_latency}
    AMIRKHANOV, B. a kol. Evaluating HTTP, MQTT over TCP
    and MQTT over WEBSOCKET for Digital Twin Applications:
    A Comparative Analysis on Latency.
    \textit{IJIRSS} [online]. 2025 [cit. 2026-03-15].
    Dostupné z: \url{https://www.ijirss.com/index.php/ijirss/article/download/4414/623/7222}
    %
    \bibitem{yokotani2016mqtt}
    YOKOTANI, T. a~SASAKI, Y.
    Comparison with HTTP and MQTT on required network
    resources for IoT.
    In: \textit{2016 International Conference on Control,
    Electronics, Renewable Energy and Communications
    (ICCEREC)} [online]. IEEE, 2016 [cit. 2026-03-15].
    Dostupné z:
    \url{https://ieeexplore.ieee.org/document/7814989}
    %
    \bibitem{mqtt_http_power}
    Comparative Analysis of Power Consumption between MQTT
    and HTTP Protocols in an IoT Platform Designed for
    Remote Real-Time Monitoring.
    \textit{PMC -- PubMed Central} [online]. 2023
    [cit. 2026-03-15].
    Dostupné z:
    \url{https://pmc.ncbi.nlm.nih.gov/articles/PMC10224120/}
    %
    \bibitem{mqtt_websocket_comparison}
    TSAQIEF, M. F. a SUTOPO, J. Comparative Performance
    Analysis Between the MQTT and WebSocket Protocols.
    \textit{bit-Tech} [online]. 2025 [cit. 2026-03-15].
    Dostupné z: \url{https://jurnal.kdi.or.id/index.php/bt/article/download/3223/1701/20910}
    %
    \bibitem{mqtt_iso_standard}
    ISO/IEC 20922:2016.
    \textit{Information Technology -- Message Queuing
    Telemetry Transport (MQTT) v3.1.1} [online].
    Geneva: IEC, 2016 [cit. 2026-03-15].
    Dostupné z: \url{https://www.iso.org/standard/69466.html}
    %
    \bibitem{mqtt_m2m_survey}
    The Use of MQTT in M2M and IoT Systems: A Survey.
    \textit{ResearchGate} [online]. 2020 [cit. 2026-03-15].
    Dostupné z: \url{https://www.researchgate.net/publication/346414150_The_Use_of_MQTT_in_M2M_and_IoT_Systems_A_Survey}
    %
    \bibitem{mqtt_lwt_review}
    MQTT Protocol for the IoT -- Review Paper.
    \textit{ResearchGate} [online]. 2023 [cit. 2026-03-15].
    Dostupné z: \url{https://www.researchgate.net/publication/373640610_MQTT_Protocol_for_the_IoT_-_Review_Paper}
    %
    \bibitem{rpi4_datasheet}
    Raspberry Pi 4 Model B -- Datasheet.
    \textit{Raspberry Pi Ltd} [online]. 2024 [cit. 2026-03-15].
    Dostupné z: \url{https://datasheets.raspberrypi.com/rpi4/raspberry-pi-4-datasheet.pdf}

    % --- Hardvér: ESP32 a mikrokontroléry ---

    \bibitem{maier2017esp32}
    MAIER, A., SHARP, A. a~VAGAPOV, Y.
    Comparative analysis and practical implementation of
    the ESP32 microcontroller module for the Internet
    of Things.
    In: \textit{Proceedings of the 7th International
    Conference on Internet Technologies and Applications
    (ITA 2017)} [online]. IEEE, 2017, s. 143--148
    [cit. 2026-03-15].
    Dostupné z:
    \url{https://ieeexplore.ieee.org/document/8101926}
    %
    \bibitem{azad2025iot}
    AZAD, T. a~kol.
    IoT edge network interoperability.
    \textit{Computer Communications} [online]. 2025,
    roč. 236, s. 108125 [cit. 2026-03-15].
    Dostupné z:
    \url{https://doi.org/10.1016/j.comcom.2025.108125}
    %
    \bibitem{darlington_vs_mosfet}
    Darlington Transistor vs. MOSFET: Selection Guidelines.
    \textit{Cadence PCB Design \& Analysis} [online]. 2023
    [cit. 2026-03-15].
    Dostupné z: \url{https://resources.pcb.cadence.com/blog/2023-pdarlington-transistor-vs-mosfet-selection-guidelines}
    %
    \bibitem{mosfet_h_bridge}
    MOSFET H-Bridge vs Dedicated Motor Driver Solutions.
    \textit{ALLPCB} [online]. 2024 [cit. 2026-03-15].
    Dostupné z: \url{https://www.allpcb.com/allelectrohub/mosfet-h-bridge-vs-dedicated-motor-driver-solutions}

    % --- Výkonová elektronika: Relé a SSR ---

    \bibitem{ssr_guide}
    Solid State Relay Guide.
    \textit{Phidgets Support} [online]. 2024
    [cit. 2026-03-15].
    Dostupné z:
    \url{https://www.phidgets.com/docs/Solid_State_Relay_Guide}
    %
    \bibitem{zero_cross_ssr}
    Zero-Cross or Random Relay: What are the Differences?
    \textit{Celduc Relais} [online]. 2024 [cit. 2026-03-15].
    Dostupné z: \url{https://www.celduc-relais.com/en/zero-cross-or-random-relay-what-are-the-differences/}
    %
    \bibitem{ssr_zero_cross_transformers}
    Beware of Zero-Crossover Switching of Transformers.
    \textit{TE Connectivity} [online]. 2024
    [cit. 2026-03-15].
    Dostupné z: \url{https://www.te.com/en/products/relays-and-contactors/electromechanical-relays/intersection/zero-crossover-switching-transformers.html}

    % --- Dátové formáty ---

    \bibitem{iot_data_formats_review}
    KAUR, A. a kol. A Literature Review on Device-to-Device
    Data Exchange Formats for IoT Applications.
    \textit{Journal of Intelligent Systems and Computing}
    [online]. 2020 [cit. 2026-03-15].
    Dostupné z: \url{https://www.researchgate.net/publication/349022302_A_Literature_Review_on_Device-to-Device_Data_Exchange_Formats_for_IoT_Applications}
    %
    \bibitem{yaml_vs_json}
    YAML vs. JSON: Definitions, Pros \& Cons.
    \textit{Built In} [online]. 2024 [cit. 2026-03-15].
    Dostupné z: \url{https://builtin.com/software-engineering-perspectives/yaml-vs-json}
    %
    \bibitem{json_xml}
    CELERDATA.
    YAML, JSON and XML: A Practical Guide to Choosing
    the Right Format.
    \textit{CelerData Blog} [online]. 2024
    [cit. 2025-02-20].
    Dostupné z: \url{https://celerdata.com/glossary/yaml-json-and-xml-a-practical-guide-to-choosing-the-right-format}
    %
    \bibitem{arduinojson_reduce_memory}
    BLANCHON, B. How to Reduce Memory Usage?
    -- ArduinoJson 7 [online]. 2026 [cit. 2026-03-15].
    Dostupné z:
    \url{https://arduinojson.org/v7/how-to/reduce-memory-usage/}
    %
    \bibitem{arduinojson_v7}
    BLANCHON, B. ArduinoJson 7 -- Release Notes [online].
    2024 [cit. 2026-03-15].
    Dostupné z: \url{https://arduinojson.org/news/2024/01/03/arduinojson-7/}

    % --- JSON ako konfiguračný jazyk pre múzejné expozície ---

    \bibitem{partarakis2016adaptable}
    PARTARAKIS, N., ANTONA, M. a STEPHANIDIS, C.
    Adaptable, personalizable and multi-user museum exhibits.
    In: \textit{Curating the Digital}. Cham: Springer, 2016,
    s. 167--179. ISBN 978-3-319-13005-9.

\end{thebibliography}